The Astropy Project

### 2017-11-11 main.tex
footnotes

Central to the success of \astropy is an open environment where anybody can
contribute to the project by opening a so-called ``pull request'' with a new
contribution on a publically available
website\footnote{\url{https://github.com/astropy/astropy}}.
This request is then reviewed by at least one of the maintainers responsible for
the specific subpackage or content and is possibly merged into the main code
base.
Most bug fixes, documentation edits, and small features are contributed in this
way.
However, this model leads to ``organic'' growth where different features are
implemented by different people with different programming styles and
interfaces.
Thus, \astropy has a mechanism to more formally propose significant changes to
the core package (e.g., the release cycle; \citealt{ape2}), to plan out major
new features, or institute new organization-wide policies (e.g.,
\citealt{ape8}).
This mechanism is called ``Astropy Proposal for Enhancement'' (APE) and are
modeled after the ``Python Enhancement Proposals'' (PEP) and guide the
development of the \python programming language.
In an APE one or more authors describe in detail the proposed changes or
additions, including a rationale for the changes, how these changes will be
implemented, and, in the case of code, what the interface will be \citep{ape1}.
The APEs are discussed and refined by the community before much work is invested
into a detailed implementation; anyone is welcome to contribute to these
discussions during the open consideration period by leaving comments on the
respective pull request.\footnote{\url{https://github.com/astropy/astropy-APEs}}
In previous APEs a community consensus emerged and APEs are accepted and become
the basis for future work at this point.
In cases where consensus cannot be reached, the
\astropy coordination committee can decide to close the discussion and
make an executive decision based on the community input on the APE in question.

>>>>

Central to the success of \astropy is an open environment where anybody can
contribute to the project by opening a so-called ``pull request'' with a new
contribution on a publically available
website.\footnote{\url{https://github.com/astropy/astropy}}
This request is then reviewed by at least one of the maintainers responsible for
the specific subpackage or content and is possibly merged into the main code
base.
Most bug fixes, documentation edits, and small features are contributed in this
way.
However, this model leads to ``organic'' growth where different features are
implemented by different people with different programming styles and
interfaces.
Thus, \astropy has a mechanism to more formally propose significant changes to
the core package (e.g., the release cycle; \citealt{ape2}), to plan out major
new features, or institute new organization-wide policies (e.g.,
\citealt{ape8}).
This mechanism is called ``Astropy Proposal for Enhancement'' (APE) and are
modeled after the ``Python Enhancement Proposals'' (PEP) and guide the
development of the \python programming language.
In an APE one or more authors describe in detail the proposed changes or
additions, including a rationale for the changes, how these changes will be
implemented, and, in the case of code, what the interface will be \citep{ape1}.
The APEs are discussed and refined by the community before much work is invested
into a detailed implementation; anyone is welcome to contribute to these
discussions during the open consideration period by leaving comments on the
respective pull request.\footnote{\url{https://github.com/astropy/astropy-APEs}}
In previous APEs a community consensus emerged and APEs are accepted and become
the basis for future work at this point.
In cases where consensus cannot be reached, the
\astropy coordination committee can decide to close the discussion and
make an executive decision based on the community input on the APE in question.
